---
output: github_document
---
<!-- badges: start -->
[![R-CMD-check](https://github.com/wurli/tweetcheck/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/wurli/tweetcheck/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

```{r setup}
#| include: FALSE
knitr::opts_chunk$set(comment = "#>")
```

# tweetcheck

{tweetcheck} is a simple R wrapper for the [twitter-text](https://github.com/twitter/twitter-text) JavaScript library which
is made available by Twitter under the Apache 2.0 license. This library allows
easy parsing of tweet text as well as autolinking and extraction of mentions.

## Installation
```{r}
#| eval: FALSE
# Install from CRAN using:
install.packages("tweetcheck")

# Install from GitHub using:
remotes::install_github("wurli/tweetcheck")
```

# Demo
## Parse tweet information

```{r}
library(tweetcheck)

tweets <- c(
  "This is a first tweet. Simple!",
  "This tweet tags @hadleywickham and @_wurli",
  "This tweet links {rtweet}: https://docs.ropensci.org/rtweet/",
  "Emojis take up two characters 😄😄😄",
  "Some may have hashtags or cashtags: #RStats $RSTATS",
  strrep("This tweet is way too long! ", 20)
)

tweet_info(tweets)
```

## Extract mentions
```{r}
tweet_get_mentions(tweets)
```

## Perform autolinking
```{r}
tweet_autolink(tweets)
```

# See also
{rtweet} is a package which allows easy interaction with the Twitter API for
actions such as posting or downloading of tweets. {V8} is a package which
allows JavaScript code to be called from R and is used by {tweetcheck}.